Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-03-05 analysis/paper/paper.Rmd
REMOVE LARGE WX COV FILE B/c >100MB

load(file = here::here('data/cov_means_daily.Rdata'))
grid_plot <- cov_means_daily %>% filter(year == 2012,
                           yday == 125) %>%
  inner_join(grid.sf, by = 'cell') %>%
  sf::st_as_sf()

>>>>

load(file = here::here('data/cov_means_daily_2102.Rdata'))
grid_plot <- cov_means_daily %>% filter(year == 2012,
                           yday == 125) %>%
  inner_join(grid.sf, by = 'cell') %>%
  sf::st_as_sf()
